% This LaTeX source code creates a resume template with a clean and professional layout.
% The document is formatted as an article and uses a 12pt Times New Roman font.

\documentclass[a4paper,12pt]{article} % Set document class, paper size, and font size.
\usepackage[T1]{fontenc} % Set font encoding.
\usepackage[utf8]{inputenc} % Set input encoding.
\usepackage{graphicx} % Package for handling images.
\usepackage[hidelinks]{hyperref} % Package for hyperlinks with hidden link borders.
\usepackage[margin=1in]{geometry} % Package for setting page margins.
\usepackage{fancyhdr} % Package for customizing headers and footers.
\usepackage{lastpage} % Package for getting the number of the last page.
\usepackage{enumitem} % Package for customizing lists.
\usepackage{xcolor} % Package for handling colors.
\usepackage{sectsty} % Package for customizing section titles.
\usepackage{titlesec} % Package for customizing section spacing.
\usepackage{times} % Package for using Times New Roman font.

\titleformat{\section}{\vspace{1em}\bfseries\scshape\Large}{}{0em}{}
\titlespacing*{\section}{0pt}{1em}{0.5em}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[RO]{\vspace{12pt}\thepage/\pageref{LastPage}}
\fancyfoot[LO]{\vspace{12pt}Updated: \today}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{20pt}

\begin{document}

\vspace{1\baselineskip}

\noindent
\begin{minipage}[t]{0.6\textwidth}
    \raggedright
    {\LARGE \textbf{Name Surname}}\\
    \vspace{1\baselineskip}
    Address\\
    Email: \href{mailto:name.surname@example.com}{name.surname@example.com}\\
    Phone: +1 (555)\\
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
    \begin{flushright}
        \vspace{2\baselineskip}
        \href{https://linkedin.com/in/name-surname}{linkedin.com/in/username}\\
        \href{https://github.com/namesurname}{github.com/username}
    \end{flushright}
\end{minipage}
\bigskip

\section*{Skills}
\begin{itemize}[leftmargin=*]
    \item Programming: Java, C++, Python, JavaScript, HTML/CSS
    \item Frameworks: React, Angular, Django
    \item Tools: Git, Docker, Jenkins, JIRA
    \item Electronics: PCB Design, Circuit Analysis, FPGA
\end{itemize}

\section*{Employment History}
\begin{itemize}[leftmargin=*]
    \item Software Engineer, ABC Tech, New York, NY, USA \hfill January 2023-Present
          \begin{itemize}
              \item Developed and maintained web applications using React, Node.js, and PostgreSQL.
              \item Collaborated with cross-functional teams to ensure high-quality code and timely delivery of features.
              \item Implemented unit tests and integration tests using Jest and Selenium.
          \end{itemize}
    \item Embedded Software Intern, XYZ Corp, San Francisco, CA, USA \hfill June 2022-August 2022
          \begin{itemize}
              \item Assisted in the development of firmware for microcontroller-based systems using C and C++.
              \item Debugged and tested embedded software using oscilloscopes, logic analyzers, and other lab equipment.
              \item Participated in code reviews and contributed to improving code quality and maintainability.
          \end{itemize}
\end{itemize}

\section*{Education}
\begin{itemize}[leftmargin=*]
    \item B.Sc. in Electronics Engineering, University Name, City, Country \hfill 2018-2022
          \begin{itemize}
              \item GPA: 3.8/4.0
              \item Relevant Courses: Data Structures and Algorithms, Operating Systems, Digital Signal Processing, Control Systems, Microelectronics, Communications Systems
              \item Senior Project: Designed and built an IoT-based home automation system using Raspberry Pi, Arduino, and various sensors.
          \end{itemize}
\end{itemize}

\section*{Projects}
\begin{itemize}[leftmargin=*]
    \item Web-Based Inventory Management System \hfill January 2022 - April 2022
          \begin{itemize}
              \item Developed a web application for managing inventory, orders, and customer information.
              \item Implemented frontend using React and backend using Django.
              \item Integrated the system with a barcode scanner for easy inventory updates.
          \end{itemize}
    \item FPGA-based Image Processing System \hfill September 2021 - December 2021
          \begin{itemize}
              \item Designed and implemented an FPGA-based image processing system for real-time object detection.
              \item Programmed the FPGA and developed a custom image processing algorithm.
              \item Optimized the system for low power consumption and high processing speed.
          \end{itemize}
\end{itemize}

\end{document}
