% This LaTeX source code creates a cover letter template with a clean and professional layout.
% The document is formatted using the article document class and a 12pt font size.

% Load necessary packages.
\documentclass[a4paper,12pt]{article} % Set document class, paper size, and font size.
\usepackage[T1]{fontenc} % Set font encoding.
\usepackage[utf8]{inputenc} % Set input encoding.
\usepackage{graphicx} % Package for handling images.
\usepackage[hidelinks]{hyperref} % Package for hyperlinks with hidden link borders.
\usepackage[margin=1in]{geometry} % Package for setting page margins.
\usepackage{fancyhdr} % Package for customizing headers and footers.
\usepackage{lastpage} % Package for getting the number of the last page.
\usepackage{enumitem} % Package for customizing lists.
\usepackage{xcolor} % Package for handling colors.
\usepackage{sectsty} % Package for customizing section titles.
\usepackage{titlesec} % Package for customizing section spacing.
\usepackage{times} % Package for using Times New Roman font.
\usepackage{lipsum} % Package for generating dummy text.
\usepackage{ragged2e} % Package for adjusting paragraph spacing.

\setlength{\headheight}{14.49998pt}

\thispagestyle{empty}

\justifying

\begin{document}

\vspace{12pt}
\vspace{12pt}

\begin{center}
    Hiring Manager's Name\\
    Hiring Manager's Position\\
    Company Name\\
    Company Address\\
    City, State, Zip Code
\end{center}

\vspace{12pt}
\vspace{12pt}

\begin{center}
    Dear Hiring Manager's Name,
\end{center}

\vspace{12pt}
\vspace{12pt}

I am writing to express my interest in the Job Title position at Company Name. With my strong background in Field/Industry, I am confident in my ability to make a significant contribution to your organization. I have gained valuable experience in Specific Skill or Experience, which I believe will make me a great fit for this role.

During my time at Previous Company/University, I successfully Specific Achievement or Responsibility. This experience allowed me to develop strong skills in Relevant Skills, e.g., problem-solving, collaboration, and communication. Furthermore, I am proficient in Programming Languages, Tools, or Technologies and have experience working in Development Environment or Context.

I am particularly excited about the opportunity to work at Company Name because of Specific Reason, e.g., company culture, innovative projects, or industry leadership. I am confident that my skills and experience align well with the requirements of the Job Title position and that I would be a valuable asset to your team.

Thank you for considering my application. I would welcome the opportunity to discuss my qualifications further and explore how my expertise can benefit Company Name. I have enclosed my resume for your review, and I can be reached at Your Email or Your Phone Number. I look forward to the possibility of working with you.

\vspace{12pt}

Sincerely,

Your Name

\end{document}
